# Data transformation

```{r results='hide',warning=FALSE}
library(tidyverse)
library(patchwork)
library(reshape2)
library(mi)
library(readr)
library(lubridate)
library(extracat)
library(ggplot2)
library(dplyr)
library(vcd)
library(RColorBrewer)
library(ggmosaic)
library(ggmap)
library(ggplot2)
library(tidyr)
library(cowplot)
library(httr)
library(rgdal)
library(tigris)
library(dplyr)
library(broom)
library(parcoords)
options(dplyr.summarise.inform=FALSE)
```

In this project, we use 5 datasets, NYPD_Arrest_Data__Historic.csv,  NYPD_Arrest_Data__Year_to_Date.csv, NYPD_Hate_Crimes.csv, COVID-19_Daily_Counts_of_Cases__Hospitalizations__and_Deaths.csv, zicode-borough.csv and Mental_Health_Service_Finder_Data.csv. 

We concentrate NYPD_Arrest_Data__Historic and NYPD_Arrest_Data__Year_to_Date to include most updated data in 2021. We convert *ARREST_DATE* to Date object and add 3 new columns *ARREST_YEAR*, *quarter* and *month* to display different statistics. In  addition, *JURISDICTION_CODE* and *AGE_GROUP* are converted to factor. Values in *OFNS_DESC* are merged according to types and mutated as the new column.

```{r}
nyc<- read_csv('NYPD_Arrests_Data__Historic_.csv')
nyc<- nyc%>%mutate(ARREST_DATE=as.Date(nyc$ARREST_DATE,format='%m/%d/%Y'))

nyc2021<-read_csv('NYPD_Arrest_Data__Year_to_Date_.csv')
nyc2021<-nyc2021%>%mutate(ARREST_DATE=as.Date(nyc2021$ARREST_DATE,format='%m/%d/%Y'))
colnames(nyc2021)[19]<- "Lon_Lat" 
nyc<-rbind(nyc,nyc2021)

nyc<- nyc%>%mutate(ARREST_YEAR= year(nyc$ARREST_DATE))

df1<-nyc%>%select(ARREST_YEAR,JURISDICTION_CODE,AGE_GROUP,PERP_SEX,OFNS_DESC,ARREST_BORO)

df1$JURISDICTION_CODE<-as.factor(df1$JURISDICTION_CODE)
levels(df1$JURISDICTION_CODE)[!(levels(df1$JURISDICTION_CODE)%in% c("0","1","2"))] <- "other"

df1<-df1%>%filter(!is.na(JURISDICTION_CODE))

df1$AGE_GROUP<-as.factor(df1$AGE_GROUP)
levels(df1$AGE_GROUP)[!(levels(df1$AGE_GROUP)%in% c("<18","18-24","25-44","45-64","65+"))] <- "unknown"
df1$AGE_GROUP<-factor(df1$AGE_GROUP,levels=c("<18","18-24","25-44","45-64","65+","unknown"))

head(df1)
```

In *NYPD_Hate_Crimes*, *DATE_OF_INTEREST* is renamed as *Date*. *ARREST_DATE* is converted to Date object. *NYPD_Hate_Crimes* is left outer joined by COVID-19_Daily_Counts_of_Cases__Hospitalizations__and_Deaths.

```{r}

covid <- read_csv("COVID-19_Daily_Counts_of_Cases__Hospitalizations__and_Deaths.csv")

covid<- covid%>%
  mutate(DATE_OF_INTEREST=as.Date(covid$DATE_OF_INTEREST,format='%m/%d/%Y'))

cdf<-covid%>%select(DATE_OF_INTEREST,CASE_COUNT,HOSPITALIZED_COUNT,DEATH_COUNT)

cdf1<-cdf%>%rename(Date=DATE_OF_INTEREST)%>%
     select(Date,CASE_COUNT)

hate<-read_csv('NYPD_Hate_Crimes.csv')

hate<- hate%>%
  mutate(Record_Date=as.Date(hate$`Record Create Date` ,format='%m/%d/%Y'))%>%
  mutate(Date=paste0(`Complaint Year Number`, "-",`Month Number`,"-1"))%>%
  mutate(Date=as.Date(Date))
hate1<-hate%>%
  group_by(`Date`)%>%
  mutate(count=n())%>%
  left_join(cdf1,by='Date')

head(hate1)
```

*Mental_Health_Service_Finder_Data* and *zicode-borough* are merged, and Borough column is counted.

```{r}
mental_data <- read_csv('Mental_Health_Service_Finder_Data.csv')
zipcode <- read_csv('zipcode-borough.csv')
df_merge = merge(x = mental_data, y = zipcode, by = "zip", all.x = TRUE)
df_mental_health = count(df_merge, Borough)
head(df_mental_health,5)
```