# Missing values
```{r setup, include=FALSE}
# this prevents package loading message from appearing in the rendered version of your problem set
knitr::opts_chunk$set(warning = FALSE, message = FALSE,
                      echo = TRUE)
library(tidyverse)
library(patchwork)
library(reshape2)

```

### DATA-1
```{r fig.width=10,fig.height=10}
source("plot_missing.R")
nyc <- read.csv("NYPD_Arrests_Data__Historic_.csv", nrows = 1000)
plot_missing(nyc, percent = TRUE)
```

Insights:
* In order to draw the picture more clearly, we select 10,000 rows of data for missing value plot.
* We can conclude that KY_CD and PD_CD have the highest percentage of missing value. Besides, X_COORD_CD, Y_COORD_CD, Latitude and Longitude belong to geographic location information and tend to miss together.
* Since the proportion of missing value for all column is small in total, so our dataset's quality is good. We may just remove the rows which has missing value when we do the following analysis.

### DATA-2
```{r fig.width=10,fig.height=10}
covid <- read.csv("COVID-19_Daily_Counts_of_Cases__Hospitalizations__and_Deaths.csv", nrows = 100)
plot_missing(covid, percent = TRUE)
```
Insights:
This is no missing value in this dataset~

### DATA-3
```{r fig.width=10,fig.height=12}
mental <- read.csv("Mental_Health_Service_Finder_Data.csv", nrows = 50)
plot_missing(mental, percent = TRUE)
```



